### 2019-08-28 manuscript/manuscript.tex
updated ms

Explain G.

@@

Finally, we observed that in the longest run evolve-and-resequence study we
analyzed \parencite{Barghi2019-qy}, some temporal covariances appeared to
become negative at future timepoints (see the first two rows in Figure
\ref{fig:figure-1} A). This could be caused by advantageous fitness backgrounds
later becoming disadvantageous, either due to frequency-dependent selection,
recombination breaking up a haplotype with coupled beneficial and deleterious
alleles, or or an environmental change in the direction of selection. However,
the signal of a change in the direction of selection may be washed out when we
calculate genome-wide temporal covariances. Averaging over such large numbers
of loci is necessary to detect a signal of covariance in allele frequency
changes when both drift (inflated in evolve-and-sequence studies which use
small population sizes) and sampling variance can create spurious covariances.
To address this limitation, we calculated temporal covariances over XXX Mb
windows, with on average XXX loci. While the covariance of each tile is noisy,
we can analyze the genome-wide distribution of tile covariances for changes
through time. We would like to compare the distribution of these tile
covariances to a neutral expectation, but a theoretically-determined neutral
null distribution would be inappropriate given complex dependencies across the
genome due to LD (which can occur over long physical distances in E&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}).

@@

\subsection{Correction}
\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/barghi-correction-plot.pdf}
  \caption{}
  \label{fig:figure-3}
\end{figure}

>>>>

\begin{center}
  \begin{tabular}{l c c c c c c}
    Study & Species & Selection & Replicates & Pop. Size & Gens. & Timepoints \\ 
  \hline
    \textcite{Kelly2019-dc}  & \emph{D. simulans} & lab & 3 & $\sim$1100 & 14 & 2 \\ \hline
    \textcite{Barghi2019-qy} & \emph{D. simulans} & lab & 10 & $\sim$1000 & 60 & 10 \\ \hline
    \textcite{Castro2019-uk} & \emph{M. musculus} & \begin{tabular}{c}tibiae length\\control\end{tabular} & \begin{tabular}{c}2\\1\end{tabular} &\begin{tabular}{c}32\\28\end{tabular}  & 20 & 2 \\
 \hline
\end{tabular}
\caption{Table to test captions and labels}
\label{table:1}
\end{center}

@@

Finally, we observed that in the longest run evolve-and-resequence study we
analyzed \parencite{Barghi2019-qy}, some temporal covariances appeared to
become negative at future timepoints (see the first two rows in Figure
\ref{fig:figure-1} A). This could be caused by advantageous fitness backgrounds
later becoming disadvantageous, either due to frequency-dependent selection,
recombination breaking up coupled beneficial and deleterious alleles, or an
environmental change in the direction of selection. However, the signal of a
change in the direction of selection localized to a particular region of the
genome may be washed out when we calculate genome-wide temporal covariances.
Averaging over such large numbers of loci is necessary to detect a signal of
covariance in allele frequency changes when both drift (inflated in
evolve-and-sequence studies which use small population sizes) and sampling
variance can create spurious covariances. To address this limitation, we
calculated temporal covariances over XXX Mb genomic windows, with on average
XXX loci per window.  While the covariance of each tile is noisy, we can
analyze the genome-wide distribution of tile covariances for changes through
time. We would like to compare the distribution of these tile covariances to a
neutral expectation, but a theoretically-determined neutral null distribution
would be inappropriate given complex dependencies across the genome due to LD
(which can occur over long physical distances in E&R and selection studies,
\cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}).

@@

\subsection{Correction}
\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/barghi-correction-plot.pdf}
  \caption{}
  \label{suppfig:correction}
\end{figure}
